Finite Property Convex Elicitation Paper

### 2019-01-25 cvx-fin.tex
Added new definition of trim and updated proof of prop 9

\begin{definition}\label{def:trim}
  \jessie{trim}
\end{definition}
\raf{Explain why this is a useful concept in general, and for convex elic}

@@

  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
\end{proposition}
\begin{proof}
For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
Thus, the set $\Theta$ generated by indexing a finite set is finite.
For $2 \implies 3$, if any level set is not full-dimensional, it is the subset of a full-dimensional level set, so we can remove it while keeping the property nondegenerate.
Thus, this set $\Theta$ is still finite, consists of full-dimensional level sets, and unions to $\simplex$

For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
Let $\R$ be the collection of such reports $u$ corresponding to each $\theta$.
The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
Since each level set is convex, we know $\gamma$ is elicitable.
\jessie{Cite Lambert 08 probably?}
\end{proof}

@@

\begin{proposition}
  If $\Gamma$ embeds $\gamma$, then there is a link function $\psi$ between $\Gamma$ and $\gamma$.
  Moreover, if $L$ elicits $\Gamma$ and $L$ is polyhedral, $\psi$ can be taken to be separated.
\end{proposition}
\begin{proof}
Let $\varphi$ be the embedding function.
Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.

For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}

>>>>

\begin{definition}\label{def:trim}
  Let $\Gamma:\simplex \toto\R'$ be a property.
  We define $\trim(\Gamma)$ as the set of full-dimensional level sets of $\Gamma$.

  Formally, $\trim(\Gamma) = \{\Gamma_u : u \in \R'\} \setminus \{ \Gamma_u : \exists w \in \R' \text{ s.t. } \Gamma_u \subset \Gamma_w \}$.
\end{definition}
\raf{Explain why this is a useful concept in general, and for convex elic}

@@

  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
\end{proposition}
\begin{proof}
  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R)\} =: \trim(\Gamma)|_{\varphi(\R)}$.
  Clearly, $\trim(\Gamma) \supseteq \trim(\Gamma)|_{\varphi(\R)}$ as we are simply restricting the number of level sets we are indexing over.
  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
  If $u \in \varphi(\R)$, then clearly we are done.
  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
  If $\Gamma_u$ is full-dimensional, it must be unique up to relabeling, giving us one of the first two cases or a contradiction of elicitability.
  If $\Gamma_u$ is not full-dimensional, it must be a subset of some full-dimensional level set, and therefore not in $\trim(\Gamma)$.
  Thus, we conclude $\trim(\Gamma) \subseteq \trim(\Gamma)|_{\varphi(\R)}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.

  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional, let us consider $\Theta := \trim(\Gamma)$.
  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
  If, for some $p \in \simplex$, there was not a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, then $\Gamma$ is degenerate.
  This can be seen since the nondegeneracy of $\Gamma$ suggests that there would have to be a level set corresponding to $w \in \R'$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.

  For $3 \implies 1$, take the set $\R$ to be the collection of reports $r$ such that $\Gamma_r \in\trim(\Gamma)$.
  (Take only one such report per level set.)
  The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
  We can then see $\gamma$ is elicitable as its level sets are all level sets of the elicitable property $\Gamma$, and therefore convex.
\end{proof}

@@

\begin{proposition}
  If $\Gamma$ embeds $\gamma$, then there is a link function $\psi$ between $\Gamma$ and $\gamma$.
  Moreover, if $L$ elicits $\Gamma$ and $L$ is polyhedral, $\psi$ can be taken to be separated.
\end{proposition}
\begin{proof}

%Let $\varphi$ be the embedding function.
%Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
%Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.
%
%For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
%If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
%If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}
